Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2020-02-16 submission/empirical2_TRfmt.tex
cleaning up
full pass, fixed lots of typos, etc.; semifinal, nearly done
minor changes

\noindent
\paragraph{Acknowledgements.}
MWM would like to acknowledge ARO, DARPA, NSF, and ONR for providing partial support of this work.
We would also like to thank Amir Khosrowshahi and colleagues at Intel for helpful discussion regarding the Group Regularization distillation technique.

\bibliographystyle{unsrt}
%\bibliographystyle{plain}
{\small
%\bibliography{gen_gap}
%\bibliography{dnns}
\bibliography{dnns,gen_gap}
}

>>>>

\vspace{-2mm}
\noindent
\paragraph{Acknowledgements.}
MWM would like to acknowledge ARO, DARPA, NSF, and ONR as well as the UC Berkeley BDD project and a gift from Intel for providing partial support of this work.
We would also like to thank Amir Khosrowshahi and colleagues at Intel for helpful discussion regarding the Group Regularization distillation technique.

\bibliographystyle{unsrt}
%\bibliographystyle{plain}
{\small
%\bibliography{gen_gap}
\bibliography{dnns}
%\bibliography{dnns,gen_gap}
}
